---
title: 'Homework 3'
subtitle: 'Due: Feb. 14, 2:30 pm'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


## Instructions
Answer each of the questions given below. Do so in a markdown file with html output.

**Submit only the HTML file.** 

Remember to `knit` often and use the techniques we discussed in class to handle code chunks with errors you cannot fix. Homework submitted in a format other than the html output from your document will not be accepted.

## Dataset
We will continue exploring the Federal Reserve's Financial Accounts of the U.S. dataset, first seen in class.

See this helpful [description of the flow of funds statements](https://www.federalreserve.gov/pubs/bulletin/2001/0701lead.pdf) (former title for this dataset). This is for background information only, e.g. on what constitutes a 'level' vs. a 'transaction.'

In particular, we will investigate consumer credit in the U.S. as given in this dataset. The **explosion in American consumer credit** is one of the major socioeconomic trends of the late 20th and early 21st centuries, and we get a little glimpse into this phenomenon here.

## Scoring
All questions worth the same amount, as with HW 1.


# Q1
Load the following two datasets

- Consumer Credit Transactions: https://raw.githubusercontent.com/brendanrbrown/brendanrbrown.github.io/master/f222.csv
- Consumer Credit Levels: https://raw.githubusercontent.com/brendanrbrown/brendanrbrown.github.io/master/l222.csv

Transactions record net value 'changing hands.' Levels record the total amount. 

For example: Say I owe you 10 dollars. In 2020 Q1 I pay back 3. Then the transaction amount is 3 dollars, and the level is 7.


# Q2 
The column names are ugly. Worse, they have different names for the same categories.

For example, both FA153166000 and FL153166000 refer to "Households and nonprofit organizations; consumer credit; liability", the former giving transactions and the latter levels.

- Using the following links for reference on names, change the column names in each of the datasets to something short and useful. See the class example for guidance.

- Remove the duplicate column for "Households and nonprofit organizations; consumer credit; liability" in each dataset.

**Your column names should match in both datasets**

Link for [transactions data](https://www.federalreserve.gov/releases/z1/20191212/html/f222.htm)
Link for [levels data](https://www.federalreserve.gov/releases/z1/20191212/html/l222.htm)

# Q3
This data is untidy: Column names are actually values of a categorical variable.

- Use a pivot function to correct the problem, as we did in class.
- Do this for each dataset
- Call your new categorical variable `series`
- In the transactions dataset, call your new values variable `transaction`
- In the levels dataset, call the new values variable `level`

**See the class example for reference.**

# Q4
We want to join these two datasets, so we can analyze levels and transactions together.

State which variable or variables can serve as key(s) for joining.

# Q5 
Join the two datasets using an appropriate join function and key, saving it as a new data frame.

Show your result by displaying the first few rows.

# Q6
Our dataset still is untidy: `date` includes two types of values.

Separate the `date` variable into two columns: `year` and `quarter`.

Be sure to use the `convert = TRUE` option.

# Q7
Convert `ND` values to `NA` and convert the `transaction` and `level` variables to numeric type if necessary.

# Q8
Choose four of the `series` categories of interest to you.

- Make two plots to demonstrate some aspect of this dataset you find interesting. The most obvious thing to do is to plot a value by year, for a given quarter. But you should do what you want.
- Make one table of summary statistics for your chosen categories.
- Write two sentences describing what the output above shows. Two sentences for the entire Q8, not two per plot and summary.