```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(cluster)
```


## Instructions
Answer each of the questions given below. Do so in a markdown file with html output.

**Submit only the HTML file.** 

Remember to `knit` often and use the techniques we discussed in class to handle code chunks with errors you cannot fix. Homework submitted in a format other than the html output from your document will not be accepted.

## Scoring
All questions worth the same amount.

## Overview
In this homework, we practice sampling and at the same time explore some properties of the $K$-means algorithm.

## Note
Since these algorithms have a randomized starting point, your results might vary somewhat substantially from one attempt to another. To avoid such problems, *set the seed before each k-means or k-mediods calculation.*

This will avoid situations in which you describe your output based on one run, only to have the plots look different after you knit.


# Q1
Generate a data frame with two columns: `x` and `y`.

`x` and `y` should be two different draws of 1000 **Normal(0, 1)** random variables.

Display the first few rows of the data frame.

# Q2
Run the $K$ means algorithm with $K=2$ on your data from Q1.

Make a scatter plot of the data, with different colors marking different clusters assigned from $K$-means.

Write two or three sentences to

- explain what the plot shows
- answer the question: Does this result make sense given what we know about the data? If so, why? If not, why not?

# Q3
Generate a second data frame with the same column names, `x` and `y`.

In this case, `x` and `y` should be two different draws of 1000 **Normal(5, 2)** random variables.

Bind the rows of this new data frame to your old one, e.g. using `bind_rows`.

# Q4
Run the $K$-means algorithm on the final dataset from Q3, with $K = 2$.

Make a scatter plot of the data, with different colors marking different clusters assigned from $K$-means.

Write two or three sentences to

- explain what the plot shows
- answer the question: Does this result make sense given what we know about the data? If so, why? If not, why not?

# Q5
Add 200 rows to your resulting data frame from Q3, such that `x = 15` and `y=15` for each of these new rows.

Run the $K$-means algorithm on this data, with $K = 2$.

Make a scatter plot of the data, with different colors marking different clusters assigned from $K$-means.

Write two or three sentences to

- explain what the plot shows
- answer the question: Does this result make sense given what we know about the data? If so, why? If not, why not?

# Q6
Create a distance matrix from your data frame used in Q5 using the `dist` function, computing distances with the `maximmum` distance. This is a built-in option in the `dist` function.

Save the distance matrix as a new object.

# Q7
Run the $K$-**mediods** algorithm using the `pam` function in the `cluster` package using $K=2$, and your distance matrix from Q6.

Make a scatter plot of the data, with different colors marking different clusters.

Write two or three sentences to

- compare this result to the one in Q5
- explain the differences, if any. Your explanation should have something to do with the different distances used.



